---
name: Tom
surname: Fiocco Walton
address: The University of Western Australia
position: PhD Candidate and Provisional Psychologist (Clinical Psychology Trainee)
pronouns: he/him
phone: 0466 726 957
email: Tom.FioccoWalton@research.uwa.edu.au
github: tfwalton
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output:
  vitae::awesomecv: default
  
---

<!-- The CV must:
1. explain any period since obtaining qualifications where you have not practised
2. be in chronological order
be signed and dated with the statemnt "This CV is true and correct as at 
be the original signed cv
-->


```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message = FALSE}
library(vitae)
library(dplyr)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

# Education and Qualifications

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Bachelor of Science with First Class Honours in Psychology. Thesis title: Sleep Discrepancy and Insomnia: An Investigation Using Polynomial Regression with Response Surface Analysis", "2020", "The University of Western Australia", "Perth, Australia",
  "Doctor of Philosophy and Master of Clinical Psychology. Thesis title: Sleep Discrepancy: A Conceptual and Methodological Investigation", "ongoing", "The University of Western Australia", "Perth, Australia",
) %>%
  detailed_entries(Degree, Year, Institution, Where)
```
# Clinical skills

- Delivery of evidence-based psychotherapy including dialectical behaviour therapy (DBT), acceptance and commitment therapy (ACT), cognitive behavioural therapy (CBT), CBT for insomnia (CBT-I), exposure with response prevention (ERP), and social skills training.
- Clinical assessment with unstructured and semi-structured interviews including risk assessment and safety planning
- Assessment with standardised psychometric instruments including measures of mental health symptomatology, emotional functioning, neurodevelopmental features, and personality inventories
- Administration, interpretation, and report writing for cognitive testing including WPPSI, WISC, WAIS, and WIAT
- Administration of neuropsychological tests including MoCA, CoCA, RBANS, DKEFS, NEPSY, WMS, WRAML

# Research skills

- Systematic review, study design, quantitative statistical analysis, and academic writing and communication
- Expertise in insomnia disorder and advanced statistical methods for analysing congruence/discrepancy in psychological constructs
- Software packages including SPSS, Visual basic for Excel, R and R Markdown including package development
- Open science practices including pre-registration and computationally reproducible manuscripts

# Procedural skills

- Working in multidisciplinary teams of medical and allied health
- Working within the NDIS system; private hospital settings; visits across clinic, school, home, and video-conference

# Awards and Prizes

```{r}
tribble(
  ~Year, ~Type,
  2020, "Australian Government Research Training Program Scholarship, awarded to support students undertaking higher degrees by research",
  2020, "Australian Psychological Society Fourth Year Prize, University of Western Australia, awarded for highest mark in fourth year psychology course",
  2020, "H.L. Fowler Prize, University of Western Australia,, awarded for best honours thesis in psychology",
) %>% brief_entries(Type, Year
                    )
  
```

# Placement Experience

```{r}

tribble(
  ~Role, ~Year, ~Company, ~Where, ~Desc,
  "Clinical Psychology Trainee", "1/03/2022 -- 15/12/2022", "The Robin Winkler Clinic", "Perth, Australia", c(
    "Provided individual cognitive behavioural therapy (CBT) and acceptance and committment therapy (ACT) for children (10+) and adults",
    "Provided neuropsychological assessments for typically and atypically ageing older adults in the Healthy Ageing Research Program (HARP)",
    "Provided brief sleep interventions for children with ADHD and other comorbid presentations",
    "Facilitated groups including CBT-I for insomnia in older adults, emotional regulation, and CBT for managing emotions",
    "Provided individual behavioural activation therapy for depression in adolescents",
    "Provided neuropsychological assessments for the Dementia prevention and risk Management Program for Aboriginal Australians project (DAMPAA)",
    "Placement was part-time comprising four days per week"
    ),

    "Clinical Psychology Trainee", "13/03/2023 -- 29/08/2023", "Ramsay Clinic Hollywood", "Perth, Australia", c(
    "Provided group therapy based in CBT, ACT, and positive psychology, and meal support as part of a outpatient eating disorders programme",
    "Provided individual psychotherapy to inpatients presenting with misuse of alcohol and other substances, severe/treatment-refractory depression,      anxiety and panic disorder",
    "Facilitated group dialectical behaviour therapy for outpatients presenting with borderline personality disorder or features thereof",
    "Placement was part-time comprising two days per week"
    ),

    "Clinical Psychology Trainee", "15/12/2023 -- 1/4/2024", "Patches Australia", "Perth, Australia", c("Provided individual psychotherapy and assessment to children (6+) and adults with neurodevelopmental disorders including Autism, ADHD, and FASD, in addition to comorbid psychological disorders", "Worked as a part of a multidisciplinary team with paediatricians, occupational therapists, speech pathologists, exercise physiologists, and physiotherapists", "Placement was part-time comprising three days per week"
  )
) %>%
  detailed_entries(Role, Year, Company, Where, Desc)
```

# Other Professional Experience

```{r}

tribble(
  ~Role, ~Year, ~Company, ~Where, ~Desc,
  
  
    "Sleep Scientist", "2013--Present", "Cardio Respiratory Sleep", "Perth, Australia", c("Polysomnography (PSG) including overnight diagnostic sleep studies, CPAP and BiPAP titrations, Multiple sleep latency test (MSLT), and maintenance of wake tests (MWT)", "Consultation with patients during trials of CPAP therapy", "Training of new staff members in PSG scoring and analysis"),
  
  "Peer Supporter", "2021-2022", "The Living Room, The University of Western Australia", "Perth, Australia", c("Provided support to UWA students with varying levels of emotional distress in a low-barrier mental health space", " Collaboratively developed self-care plans, safety plans with Living Room guests; conducted brief interventions (sleep, alcohol)"
    )
  )%>%
  detailed_entries(Role, Year, Company, Where, Desc)
```

# Teaching experience

```{r}

tribble(
  ~Role, ~Year, ~Company, ~Where, ~Desc,
  "Laboratory Demonstrator", "2021--2022", "School of Psychological Science, The University of Western Australia", "Perth, Australia", c("Psychology: Mind and Brain (PSYC1101)", "Adult Psychopathology (PSYC2214)", "Introduction to Quantitative Methods in Psychology (PSYC2203)"
    )
  )%>%
  detailed_entries(Role, Year, Company, Where, Desc)
```

# Volunteer experience

```{r}

tribble(
  ~Role, ~Year, ~Company, ~Where, ~Desc,
  "Fit for Study Peer Educator", "2019--2021", "Health Promotion Unit, The University of Western Australia", "Perth, Australia", c("Participation in outreach education and wellbeing programmes at university events and colleges including brief alcohol interventions; sexuality, sexual health, and relationships, mental wellbeing"
    )
  )%>%
  detailed_entries(Role, Year, Company, Where, Desc)
```

